Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-16 wpe.tex
fixing wpe
added an intro paragraph to the wpe section

\section{Measuring Structural Complexity }\label{sec:meaComplex}
{\color{red} NOT EDITABLE}

THINGS TO DO
\begin{enumerate}
\item rewrite for consistency in notation. For example, some parts of the paper call word length $l$ and some call it $n$.

\item make sure it is clear and we justify that detecting and characterizing structural complexity is hard for real-valued noisy time series.
\item Quantifying structured and unstructured complexity is nontrivial in the case of real-valued noisy time series but WPE does this. [[talk about again here but justify in information theory section]]
\item justify and explain the regime split in \svd {\color{red} I(joshua) moved this justification in the experimental methods section, it just needs to be explored here by applying windowed wpe and explaining that method}
\end{enumerate}

>>>>

\section{Measuring Structural Complexity }\label{sec:meaComplex}
{\color{blue} EDITABLE}

The goal of the section is to describe how we reasonably estimate the entropy of an arbitrary, real-valued time series. We will first detail why this is a highly non-trivial task, and then we will weave a path through which this can in fact be accomplished. This path will draw upon a myriad of tools and results from a variety of fields including time series analysis, dynamical systems, stochastic processes, and chaos.
